Modalities for Location Virtualization

### 2022-09-20 intro.tex
a couple notes

This kind of context-dependent assertion, where a fact may be true in one address space but not others, has a modal flavor. We propose tackling the verification of virtual memory subsystems (and kernels more broadly) by adapting ideas from hybrid modal logic, which can label assertions true under \emph{other} circumstances (i.e., in another address space) with a modality indexed by a name for that space (in our case, the root of the page tables for an address space). This offers a convenient and powerful way to modularly (1) isolate assertions specific to a particular address space, and (2) explicitly state when an assertion is true across address spaces.

>>>>

This kind of context-dependent assertion, where a fact may be true in one address space but not others, has a modal flavor. We propose tackling the verification of virtual memory subsystems (and kernels more broadly) by adapting ideas from hybrid modal logic, which can label assertions true under \emph{other} circumstances (i.e., in another address space) with a modality indexed by a name for that space (in our case, the root of the page tables for an address space). This offers a convenient and powerful way to modularly (1) isolate assertions specific to a particular address space, (2) explicitly state when an assertion is true across address spaces, (3) manipulate address spaces from within other address spaces, and (4) reason about change in address spaces. These advantages make this approach to reasoning about virtual memory more flexible than prior program logic techniques~\cite{kolanski08vstte,kolanski09tphols}, which was only able to work with a single address space (the current address space on the CPU).

### 2022-09-20 semantics.tex
+
a couple notes

@@

\subsection{Indexed Memory \& Register by References}

@@

In fact $\readlval\maddr{\storememstar\crval}\locsf$ is unfoled into multiple physical memory lookups for the final page address retrieval -- i.e. address translation traversal. 

>>>>

\todo[inline]{I don't think we need or want to describe the operational semantics in detail in the submission. It adds a lot of formalization that doen'st necessarily contribute to reader understanding. We should describe the runtime \emph{state} $\sigma$ of memory and registers, since that is directly used in interpreting assertions. But the reduction rules will mostly add mental overhead here.}

@@

\subsection{Memory Addresses \& Naming Registers}

@@

In fact $\readlval\maddr{\storememstar\crval}\locsf$ is unfoled into multiple physical memory lookups for the final page address retrieval -- i.e. address translation traversal as shown in Figure \ref{fig:pagetables}  \mytodo{1.address more about the challenging aspects of this traversal and the last level update}
